---
title: "AI UK Demonstration"
output: html_document
date: "`r Sys.Date()`"
---

# Solution

This document demonstrates one way to solve the challenge using R.

## Libraries

We're going to use the `tidyverse` suite of packages for this exercise.

Different security tiers of the Data Safe Haven support installing packages in different ways.

- Tier ≤ 2: Able to install any package from PyPI and CRAN
- Tier 3: Able to install a configurable, curated list of packages from PyPI and CRAN

In addition, for R some packages beyond the default packages (those collectively called `base` R) are installed automatically, so we don't have to install them here.

Let's load the `tidyverse` packages.

```{r load-packages}
library(tidyverse)
```

## Find the data  

In a Data Safe Haven environment, the input data is located at `/data/`.

```{bash list-data-folder}
ls /data
```

The `/data` directory and the files within it are read-only.

This preserves the integrity of input data.

We can test this by trying to write to `/data` and to append data to `/data/data.csv'.

```{bash create-demo, error = TRUE}
touch /data/new_file.txt
echo "hello" >> /data/data.csv
```

## Inspect the data

We will read the data from the `csv` file and store it in a `data.frame`.

```{r load-data}
df <- read_csv("/data/data.csv")
```

We want to calculate the **mean height**.

Let's look at the column names to see if we can find which column contains the height data.

```{r column-names}
colnames(df)
```

We could go ahead and calculate the mean immediately:

```{r calc-mean, eval = FALSE}
mean(df$height)
```

However, we should look at the data first to check whether it makes sense.

First, let's get a summary of the height column.

```{r get-summary}
height <- df$height 

summary(height)
```

The mean looks reasonable.

168.8 would make sense if the height values are in cm.

But look at the minimum and maximum values.
Those don't seem reasonable at all.

Let's look closer at the smallest values.

```{r sort-height}
height_sorted <- sort(height)
head(height_sorted, 10)
```

And then let's look at the largest values.

```{r tail-height}
tail(height_sorted, 10)
```

## Cleaning the data

It would be more reasonable to remove these outliers.

Here, we will use information about how those outliers were generated to remove them.

The anomalously large heights are always greater than or equal to 1000.
The anomalously smaller heights are always less than 10.

```{r filter-height}
height_filtered <- height[height < 1000 & height >= 10]
```

## Calculating the mean

Now we can calculate the mean of our cleaned height data.

```{r mean-height}
mean_height <- round(mean(height_filtered), 1)
mean_height
```

## Prepare your result for extraction

In a Data Safe Haven environment data in `/output` can be considered for removing from the environment.

You can read, write and delete files in the `/output` directory.

```{bash create-file}
ls /output
echo "hello" >> /output/a.txt
cat /output/a.txt
```

If we write our output to a file in `/output` an admin will be able to create a link to download that file after the review process is completed.

```{r write-output}
writeLines(as.character(mean_height),
           "/output/mean_height.txt")
```

```{bash check-output}
cat /output/mean_height.txt
```


